Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-01-31 Methods-and-Results.Rmd
adjusted

```{r workerOutModelMLQltNull, include=FALSE}
# Create and save Model
mdlWorkerOut$Qlt$lmerNull <-
  lme4::lmer(quality_overall_1 ~ 1 + (1 | PID), 
             data = dtWorkerSupp$workerOutWithinBetween) # use optim if it does not converge
mdlWorkerOut$Qlt$lmeNull <-
  mdlWorkerOut$Qlt$lmeNull <-lme(
    quality_overall_1 ~ 1,
    random = ~ 1 | PID,
    data = dtWorkerSupp$workerOutWithinBetween,
    na.action=na.omit,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

@@

mdlWorkerOut$Qlt$lmerInterceptCoreCI <- 
  confint(method = "Wald", mdlWorkerOut$Qlt$lmerInterceptCore)

@@

mdlWorkerOut$Qlt$lmerSlopesCoreCI <- 
  confint(method = "Wald", mdlWorkerOut$Qlt$lmerSlopesCore)

@@

mdlWorkerOut$Att$lmerInterceptCoreQltCI <- 
  confint(method = "Wald", mdlWorkerOut$Att$lmerInterceptCoreQlt)

@@

mdlWorkerOut$Att$lmerSlopesCoreQltCI <- 
  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreQlt)

@@

mdlWorker$lmerInterceptAttCoreIntCI <- 
  confint(method = "Wald", mdlWorker$lmerInterceptAttCoreInt)

>>>>

```{r workerOutModelMLQltNull, include=FALSE}
# Create and save Model
mdlWorkerOut$Qlt$lmerNull <-
  lme4::lmer(quality_overall_1 ~ 1 + (1 | PID), 
             data = dtWorkerSupp$workerOutWithinBetween) # use optim if it does not converge

mdlWorkerOut$Qlt$lmeNull <-
  mdlWorkerOut$Qlt$lmeNull <- lme(
    quality_overall_1 ~ 1,
    random = ~ 1 | PID,
    data = dtWorkerSupp$workerOutWithinBetween,
    na.action=na.omit,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

@@

# 95%CI
mdlWorkerOut$Qlt$lmerInterceptCoreCI <- 
  confint(method = "Wald", mdlWorkerOut$Qlt$lmerInterceptCore)

@@

# 95%CI
mdlWorkerOut$Qlt$lmerSlopesCoreCI <- 
  confint(method = "Wald", mdlWorkerOut$Qlt$lmerSlopesCore)

@@

# 95% CI
mdlWorkerOut$Att$lmerInterceptCoreQltCI <- 
  confint(method = "Wald", mdlWorkerOut$Att$lmerInterceptCoreQlt)

@@

# 95%CI
mdlWorkerOut$Att$lmerSlopesCoreQltCI <- 
  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreQlt)

@@

# 95%CI
mdlWorker$lmerInterceptAttCoreIntCI <- 
  confint(method = "Wald", mdlWorker$lmerInterceptAttCoreInt)
